---
title: "Fear Conditioning"
author: "Anna MacFarlane"
date: "1/31/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(cowplot)
library(gplots)
library(ggplot2)
library(patternplot)
library(lme4)
library(visreg)
library(tidyr)
library(magrittr) 
library(dplyr)
library(ggpubr)
library(lme4)
library(lsmeans)
library(emmeans)
library(zoo)

batch1_0<-read.csv('FC_data/Batch1/Batch_day0_201026_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch1_1<-read.csv('FC_data/Batch1/Batch_day1_211026_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch1_2<-read.csv('FC_data/Batch1/Batch_day2_211026_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch2_0<-read.csv('FC_data/Batch2/Batch_day0_210118_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch2_1<-read.csv('FC_data/Batch2/Batch_day1_210118_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch2_2<-read.csv('FC_data/Batch2/Batch_day2_210118_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch3_0<-read.csv('FC_data/Batch3/Batch_day0_210212_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch3_1<-read.csv('FC_data/Batch3/Batch_day1_210222_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch3_2<-read.csv('FC_data/Batch3/Batch_day2_210212_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch4_0<-read.csv('FC_data/Batch4/Batch_day0_210201_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch4_1<-read.csv('FC_data/Batch4/Batch_day1_210201_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch4_2<-read.csv('FC_data/Batch4/Batch_day2_210201_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch5_0<-read.csv('FC_data/Batch5/Batch_day0_210222_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch5_1<-read.csv('FC_data/Batch5/Batch_day1_210222_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch5_2<-read.csv('FC_data/Batch5/Batch_day2_210222_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch6_0<-read.csv('FC_data/Batch6/Batch_day0_210503_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch6_1<-read.csv('FC_data/Batch6/Batch_day1_210503_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch6_2<-read.csv('FC_data/Batch6/Batch_day2_210503_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch7_0<-read.csv('FC_data/Batch7/Batch_day0_210614_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch7_1<-read.csv('FC_data/Batch7/Batch_day1_210614_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch7_2<-read.csv('FC_data/Batch7/Batch_day2_210614_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch8_0<-read.csv('FC_data/Batch8/Batch_day0_210809_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch8_1<-read.csv('FC_data/Batch8/Batch_day1_210809_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch8_2<-read.csv('FC_data/Batch8/Batch_day2_210809_15Motionthreshold_10_minfreezeduration.csv', skip=13)

batch9_0<-read.csv('FC_data/Batch9/Batch_day0_210906_SeptMixed_15Motionthreshold_10minfreezeduration.csv', skip=16)
batch9_1<-read.csv('FC_data/Batch9/Batch_day1_210906_SeptMixed_15Motionthreshold_10minfreezeduration.csv', skip=11)
batch9_2<-read.csv('FC_data/Batch9/Batch_day2_210906_SeptMixed_15Motionthreshold_10minfreezeduration.csv', skip=13)

batch10_0<-read.csv('FC_data/Batch10/Batch_day0_211004OctMixed_15Motionthreshold_10minfreezeduration.csv', skip=16)
batch10_1<-read.csv('FC_data/Batch10/Batch_day1_211004OctMixed_15Motionthreshold_10minfreezeduration.csv', skip=11)
batch10_2<-read.csv('FC_data/Batch10/Batch_day2_211004OctMixed_15Motionthreshold_10minfreezeduration.csv', skip=13)

batch11_0<-read.csv('FC_data/Batch11/Batch_day0_211122NovMixed_15Motionthreshold_10minfreezeduration.csv', skip=16)
batch11_1<-read.csv('FC_data/Batch11/Batch_day1_211122NovMixed_15Motionthreshold_10minfreezeduration.csv', skip=11)
batch11_2<-read.csv('FC_data/Batch11/Batch_day2_211122NovMixed_15Motionthreshold_10minfreezeduration.csv',skip=13)

batch12_0<-read.csv('FC_data/Batch12/Batch_day0_220110JanMix_15MotionThreshold_10MinFreezeDuration.csv', skip=16)
batch12_1<-read.csv('FC_data/Batch12/Batch_day1_220110JanMix_15MotionThreshold_10MinFreezeDuration.csv', skip=11)
batch12_2<-read.csv('FC_data/Batch12/Batch_day2_220110JanMix_15MotionThreshold_10MinFreezeDuration.csv',skip=13)

batch13_0<-read.csv('FC_data/Batch13/Batch_Day0_220207Feb2022_15MotionThreshold_10Minfreezeduration.csv', skip=16)
batch13_1<-read.csv('FC_data/Batch13/Batch_Day1_220207Feb2022_15MotionThreshold_10Minfreezeduration.csv', skip=11)
batch13_2<-read.csv('FC_data/Batch13/Batch_Day2_220207Feb2022_15MotionThreshold_10Minfreezeduration.csv',skip=13)

batch14_0<-read.csv('FC_data/Batch14/Batch_Day0_220307March2022_15MotionThreshold_10minfreezeduration.csv', skip=16)
batch14_1<-read.csv('FC_data/Batch14/Batch_Day1_220307March2022_15MotionThreshold_10minfreezeduration.csv', skip=11)
batch14_2<-read.csv('FC_data/Batch14/Batch_Day2_220307March2022_15MotionThreshold_10minfreezeduration.csv',skip=13)

batch15_0<-read.csv('FC_data/Batch15/Batch_day0_220404_April2022_15motionthreshold_10minfreezeduration.csv', skip=16)
batch15_1<-read.csv('FC_data/Batch15/Batch_day1_220404_April2022_15motionthreshold_10minfreezeduration.csv', skip=11)
batch15_2<-read.csv('FC_data/Batch15/Batch_day2_220404_April2022_15motionthreshold_10minfreezeduration.csv',skip=13)

batch16_0<-read.csv('FC_data/Batch16/Batch_day0_220509_May2022_15motionthreshold_10minfreezeduration.csv', skip=16)
batch16_1<-read.csv('FC_data/Batch16/Batch_day1_220509_May2022_15motionthreshold_10minfreezeduration.csv', skip=11)
batch16_2<-read.csv('FC_data/Batch16/Batch_day2_220509_May2022_15motionthreshold_10minfreezeduration.csv',skip=13)

batch17_0<-read.csv('FC_data/Batch17/Batch_Day0_220606_June2022_15MotionThreshold_10MinFreezeDuration.csv', skip=16)
batch17_1<-read.csv('FC_data/Batch17/Batch_Day1_220606_June2022_15MotionThreshold_10MinFreezeDuration.csv', skip=11)
batch17_2<-read.csv('FC_data/Batch17/Batch_Day2_220606_June2022_15MotionThreshold_10MinFreezeDuration.csv',skip=13)

batch18_0<-read.csv('FC_data/Batch18/220704_Day0_July18monthHFD_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch18_1<-read.csv('FC_data/Batch18/220704_Day1_July18monthHFD_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch18_2<-read.csv('FC_data/Batch18/220704_Day2_July18monthHFD_15Motionthreshold_10_minfreezeduration.csv',skip=13)

batch19_0<-read.csv('FC_data/Batch19/Batch_Day0_220808August2022_15Motionthreshold_10_minifreezeduration.csv', skip=16)
batch19_1<-read.csv('FC_data/Batch19/Batch_Day1_220808August2022_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch19_2<-read.csv('FC_data/Batch19/Batch_Day2_220808August2022_15Motionthreshold_10_minfreezeduration.csv',skip=13)

batch20_0<-read.csv('FC_data/Batch20/Batch_day0_220905September2022_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch20_1<-read.csv('FC_data/Batch20/Batch_day1_220905September2022_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch20_2<-read.csv('FC_data/Batch20/Batch_day2_220905September2022_15Motionthreshold_10_minfreezeduration.csv',skip=13)

colnames(batch20_0)[1] ='Animal_ID'

batch21_0<-read.csv('FC_data/Batch21/Batch_day0_221003October2022_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch21_1<-read.csv('FC_data/Batch21/Batch_day1_221003October2022_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch21_2<-read.csv('FC_data/Batch21/Batch_day2_221003October2022_15Motionthreshold_10_minfreezeduration.csv',skip=13)

colnames(batch21_0)[1] ='Animal_ID'
colnames(batch21_1)[1] ='Animal_ID'
colnames(batch21_2)[1] ='Animal_ID'

batch21_0 = subset(batch21_0, select = -c(15, 16, 17) )

batch22_0<-read.csv('FC_data/Batch22/Batch_Day0_221101November22_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch22_1<-read.csv('FC_data/Batch22/Batch_Day1_221101November22_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch22_2<-read.csv('FC_data/Batch22/Batch_Day2_221101November22_15Motionthreshold_10_minfreezeduration.csv',skip=13)

batch23_0<-read.csv('FC_data/Batch23/Batch_Day0_221128_December22_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch23_1<-read.csv('FC_data/Batch23/Batch_Day1_221128December22_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch23_2<-read.csv('FC_data/Batch23/Batch_Day2_221128December22_15Motionthreshold_10_minfreezeduration.csv',skip=13)

colnames(batch23_0)[1] ='Animal_ID'
colnames(batch23_1)[1] ='Animal_ID'
colnames(batch23_2)[1] ='Animal_ID'

batch24_0<-read.csv('FC_data/Batch24/Batch_Day0_230117_January23_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch24_1<-read.csv('FC_data/Batch24/Batch_Day1_230117_January23_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch24_2<-read.csv('FC_data/Batch24/Batch_Day2_230117_January23_15Motionthreshold_10_minfreezeduration.csv',skip=13)

colnames(batch24_0)[1] ='Animal_ID'
colnames(batch24_1)[1] ='Animal_ID'
colnames(batch24_2)[1] ='Animal_ID'

batch25_0<-read.csv('FC_data/Batch25/Batch_Day0_230213_February23_15Motionthreshold_10_minfreezeduration.csv', skip=16)
batch25_1<-read.csv('FC_data/Batch25/Batch_Day1_230213_February23_15Motionthreshold_10_minfreezeduration.csv', skip=11)
batch25_2<-read.csv('FC_data/Batch25/Batch_Day2_230213_February23_15Motionthreshold_10_minfreezeduration.csv',skip=13)
 
#day0_comp <- read.csv('day0_10_minfreezeduration_compiled.csv')
#day1_comp <- read.csv('day1_10_minfreezeduration_compiled.csv')
#day2_comp <- read.csv('day2_10_minfreezeduration_compiled.csv')

add0 <- rbind(batch1_0, batch2_0, batch3_0, batch4_0, batch5_0, 
              batch6_0, batch7_0, batch8_0, batch9_0, batch10_0, batch11_0, 
              batch12_0, batch13_0, batch14_0, batch15_0, batch16_0, batch17_0, 
              batch18_0, batch19_0, batch20_0, batch21_0, batch22_0,
              batch23_0, batch24_0, batch25_0)
add1 <- rbind(batch1_1, batch2_1, batch3_1, batch4_1, batch5_1, 
              batch6_1, batch7_1, batch8_1, batch9_1, batch10_1, batch11_1,
              batch12_1, batch13_1, batch14_1, batch15_1, batch16_1,
              batch17_1, batch18_1, batch19_1, batch20_1, batch21_1, batch22_1,
              batch23_1, batch24_1, batch25_1)
add2 <- rbind(batch1_2, batch2_2, batch3_2, batch4_2, batch5_2, 
              batch6_2, batch7_2, batch8_2, batch9_2, batch10_2, batch11_2,
              batch12_2, batch13_2, batch14_2, batch15_2, batch16_2,
              batch17_2, batch18_2, batch19_2, batch20_2, batch21_2, batch22_2,
              batch23_2, batch24_2, batch25_2)

#animal_info <- read.csv('updated.csv')
animal_info <- read.csv('qial_animals_with_age2.csv')


all_day2 <- left_join(add2, animal_info, by = c("Animal_ID" = "BadeaID"))
all_day1 <- left_join(add1, animal_info, by = c("Animal_ID" = "BadeaID"))
all_day0 <- left_join(add0, animal_info, by = c("Animal_ID" = "BadeaID"))

all_day0<-all_day0 %>% 
  filter(Animal_ID!='') %>% 
  mutate(Age_group = case_when(
    Age_Months <= 16 ~ 'Young',
    Age_Months > 16 ~ 'Old'
  ))
  
all_day1<-all_day1 %>% 
  filter(Animal_ID!='') %>% 
  mutate(Age_group = case_when(
    Age_Months <= 16 ~ 'Young',
    Age_Months > 16 ~ 'Old'
  ))

all_day2<-all_day2 %>% 
  filter(Animal_ID!='') %>% 
  mutate(Age_group = case_when(
    Age_Months <= 16 ~ 'Young',
    Age_Months > 16 ~ 'Old'
  ))



```


```{r help}
day0_lmer<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time!=0) 
  #filter(Age_group == '6 months') %>% 
  filter(!is.na(Age_group)) %>% 
  filter(Treatment =='Control') %>% 
  group_by(Genotype, Time) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

print(day0_lmer)

all_animals <-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN" |
           Genotype == "APOE22" |
           Genotype == "APOE33" |
           Genotype == "APOE44") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time!=0) %>%  
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'female ' ~ 'Female',
  )) %>% 
  filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group))

animal_counts<-distinct(all_animals, Animal_ID, .keep_all = TRUE)
animal_counts<-animal_counts[!is.na(animal_counts$Sex), ]
table(animal_counts$Genotype)

table(animal_counts[animal_counts$Genotype == 'APOE22', ]$Sex)

table(animal_counts$Genotype)

```

```{r day-0-data}

test_counts<-all_day0 %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>%  
  filter(Age_group == '12 months') %>% 
  filter(Component.Name == 'Sound 1') %>% 
  count(Treatment)

animal_counts_fc<-distinct(all_day0, Animal_ID, .keep_all = TRUE)
table(animal_counts_fc$Genotype)

day0_lmer<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time!=0) %>% 
  mutate(Age_group = case_when(
    Age_Substracted < 9 ~ '6 months',
    Age_Substracted >= 9 | Age_Substracted <= 16 ~ '12 months',
    Age_Substracted >= 16 ~ "18 months"
  )) %>% 
  filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  group_by(Genotype, Treatment, Time) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

print(day0_lmer)

day0<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE44HN") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  ))  %>%  
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  group_by(Genotype, Treatment, Time) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) %>% 
  count(Genotype)

day0_test<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time!=0) %>%  
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  #filter(Age_group == '12 months') %>% 
  select(Genotype, Time, Animal_ID, 
         Treatment, Pct.Total.Time.Freezing) 

print(day0_test)

 # geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5)+
 # theme_bw() + 
 # labs(title="Learning Curve", x="Time", 
 #      y='Mean Percent Time Freezing', 
 #      legend='Genotype') +
 # scale_x_continuous(breaks=c(1, 2, 3)) +
 # scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000"))



# faceted by diet, only HN genotypes

hn_group <- all_day0 %>% 
  filter(!is.na(Animal_ID)) %>%
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>%  
  #filter(Age_group == '12 months') %>% 
  filter(Time != 0 ) %>% 
  group_by(Genotype, Treatment, Time) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

hn_sex<- all_day0 %>% 
  filter(!is.na(Animal_ID)) %>%
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  mutate(Age_group = case_when(
    Age_Substracted < 9 ~ '6 months',
    Age_Substracted >= 9 | Age_Substracted <= 16 ~ '12 months',
    Age_Substracted >= 16 ~ "18 months"
  )) %>%  
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  filter(!is.na(Sex)) %>% 
  #filter(Age_group == '12 months') %>% 
  filter(Time != 0 ) %>% 
  group_by(Genotype, Treatment, Time, Sex) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

counts <- hn_group %>% 
  count(Genotype)
print(counts)

# 33 and 44 comparisons 

# RUN THIS FOR BASIC LINES
# took out treatment, and added age group 
nonHN<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time == 1 |
           Time == 2 |
           Time == 3)  %>%  
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  group_by(Genotype, Age_group, Time) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing))  

nonHN1<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time == 1 |
           Time == 2 |
           Time == 3) %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Treatment)) %>% 
  group_by(Genotype, Treatment, Time) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

```

```{r cross-model-comparisons}
day0_22<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE22") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time!=0) %>% 
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  #filter(Age_group == '12 months') %>% 
  select(Genotype, Time, Animal_ID, Age_group,
         Treatment, Pct.Total.Time.Freezing) %>% 
  mutate(Treatment = case_when(
      Treatment=='HFD' ~ 'High Fat Diet',
      Treatment=='Control'~ 'Control'
  ))  %>% 
  filter(Time != 0 ) %>% 
  group_by(Genotype, Treatment, Time, Age_group) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 


ggplot(data=day0_22, aes(x=Time, y=len, color=Age_group)) +
  geom_line(stat="identity", width=0.5) +
  facet_grid(.~Genotype) + 
  labs(y="Average Percent Freezing Time", x='Component') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5)+
  theme_bw() + 
  labs(title="Learning Curve", x="Time", 
       y='Mean Percent Time Freezing', 
       legend='Genotype') +
  scale_x_continuous(breaks=c(1, 2, 3)) +
  scale_color_manual(values = c("#6a0dad", "#1BCC97"))

ggplot(data=day0_22, aes(x=Time, y=len, color=Genotype)) +
  geom_line(stat="identity", width=0.5) +
  facet_grid(.~Age_group) + 
  labs(y="Average Percent Freezing Time", x='Component') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5)+
  theme_bw() + 
  labs(title="Learning Curve", x="Time", 
       y='Mean Percent Time Freezing', 
       legend='Genotype') +
  scale_x_continuous(breaks=c(1, 2, 3)) +
  scale_color_manual(values = c("#6a0dad", "#1BCC97"))
```
```

```{r day-0-graphs}

# faceted by diet, only HN genotypes

poster<-hn_group %>% 
  mutate(Treatment = case_when(
      Treatment=='HFD' ~ 'High Fat Diet',
      Treatment=='Control'~ 'Control'
  ))

nonHN<-nonHN %>% 
  mutate(Treatment = case_when(
      Treatment=='HFD' ~ 'High Fat Diet',
      Treatment=='Control'~ 'Control'
  ))

ggplot(data=hn_sex, aes(x=Time, y=len, color=Genotype)) +
  geom_line(stat="identity", width=0.5) +
  facet_grid(Sex~Treatment) + 
  labs(y="Average Percent Freezing Time", x='Component') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5)+
  theme_bw() + 
  labs(title="Learning Curve", x="Time", 
       y='Mean Percent Time Freezing', 
       legend='Genotype') +
  scale_x_continuous(breaks=c(1, 2, 3)) +
  scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000"))

# figure for paper HN
ggplot(data=poster, aes(x=Time, y=len, color=Genotype)) +
  geom_line(stat="identity", width=0.5) +
  facet_grid(.~Treatment) + 
  labs(y="Average Percent Freezing Time", x='Component') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5)+
  theme_bw() + 
  labs(title="Learning Curve", x="Time", 
       y='Mean Percent Time Freezing', 
       legend='Genotype') +
  scale_x_continuous(breaks=c(1, 2, 3)) +
  scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000"))

# figure for paper non HN
ggplot(data=nonHN, aes(x=Time, y=len, color=Age_group)) +
  geom_line(stat="identity", width=0.5) +
  facet_grid(.~Genotype) + 
  labs(y="Average Percent Freezing Time", x='Component') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5)+
  theme_bw() + 
  labs(title="Learning Curve", x="Time", 
       y='Mean Percent Time Freezing', 
       legend='Age_group') +
  scale_x_continuous(breaks=c(1, 2, 3)) +
  scale_color_manual(values = c("#1BCC97", "#1B50CC", "#CC1BA8"))

# non HN faceted by age group
  ggplot(data=nonHN, aes(x=Time, y=len, color=Genotype)) +
  geom_line(stat="identity") +
  facet_grid(.~Treatment) + 
  labs(y="Average Percent Freezing Time", x='Component') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5)+
  theme_bw() + 
  labs(title="Learning Curve", x="Time", 
       y='Mean Percent Time Freezing', 
       legend='Genotype') +
  scale_x_continuous(breaks=c(1, 2, 3)) +
  scale_color_manual(values = c("#1BCC97", "#1B50CC", "#CC1BA8"))


ggline(day0_test, x='Time', y='Pct.Total.Time.Freezing',
       color='Genotype', fill='Genotype', facet.by=c('Treatment'), 
       error.plot='errorbar', add='mean_se',
       palette = c("#6a0dad", "#008000", "#FF0000"), size=1,
       point.size=1.5, legend='top')


ggline(nonHN, x='Time', y='Pct.Total.Time.Freezing',
       color='Genotype', fill='Genotype', facet.by=c('Treatment'), 
       error.plot='errorbar', add='mean_se',
       palette = c("#1BCC97", "#1B50CC", "#CC1BA8"), size=1,
       point.size=1.5, legend='top')


```

```{r day-0-anova}

# just analyzing differences between HN

day0_lmer<-all_day0 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  mutate(Time = case_when(
    Component.Name == 'Sound 1' ~ 1,
    Component.Name == 'Shock 1' ~ 0,
    Component.Name == 'Sound 2' ~ 2,
    Component.Name == 'Shock 2' ~ 0,
    Component.Name == 'Sound 3' ~ 3,
    Component.Name == 'Shock 3' ~ 0,
  )) %>% 
  filter(Time!=0) %>% 
  mutate(Age_group = case_when(
    Age_Substracted < 9 ~ '6 months',
    Age_Substracted >= 9 | Age_Substracted <= 16 ~ '12 months',
    Age_Substracted >= 16 ~ "18 months"
  )) %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  select( Animal_ID, Genotype, Treatment, 
          Time, Pct.Total.Time.Freezing) 

print(day0_lmer)

#%>% 
#  group_by(Genotype, Treatment, Time, Animal_ID, Sex) %>% 
#  summarise(n=n(),
#            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
 #           len = mean(Pct.Total.Time.Freezing)) 

day0_HFD<-day0_lmer %>% 
  filter(Treatment=='HFD')
day0_control<-day0_lmer %>% 
  filter(Treatment=='Control')

mod1<-lmer(Pct.Total.Time.Freezing~factor(Genotype)*Time+(1|Animal_ID), day0_HFD)
mod2<-lmer(Pct.Total.Time.Freezing~factor(Genotype)*Time+(1|Animal_ID), day0_control)

mix1<-emmeans(mod1, "Genotype", adjust = "Tukey")
mix2<-emmeans(mod2, "Genotype", adjust = "Tukey")

pairs(mix1)
pairs(mix2)

a1<-anova(mod1)
a2<-anova(mod2)

#a1
#a2

```

```{r help-2}
day1_lm<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  filter(Treatment=="Control") %>% 
  group_by(Genotype, Treatment) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 
print(day1_lm)
```

```{r day-1-data}
# all animals
counts<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>%  
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  select(Genotype, Sex, Treatment) 

day1_lm<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22" |
           Genotype == "APOE44HN")  %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  select(Genotype, Sex, Treatment) 

day1<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE44HN" |
           Genotype == "APOE22") %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  group_by(Genotype, Age_group, Treatment) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 


# HNs
  
day1HN<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  #filter(Age_group == '12 months') %>% 
  group_by(Genotype, Treatment) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing))

  
day1HN_sex<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
    #mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  filter(!is.na(Sex)) %>% 
  filter(Age_group == '12 months') %>% 
  group_by(Genotype, Treatment, Sex) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing))

print(day1HN_sex)

# non HN (added age group, took out treatment)
day1_nonHN<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22") %>% 
  #filter(Age_group == '12 months') %>% 
  mutate(Treatment = case_when(
      Treatment=='HFD' ~ 'High Fat Diet',
      Treatment=='Control'~ 'Control'
  )) %>% 
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  filter(!is.na(Sex)) %>% 
  filter(!is.na(Age_group)) %>% 
  group_by(Genotype, Age_group, Sex) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing))  


nonHN2<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == 'APOE22') %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  group_by(Genotype, Age_group) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 
```

```{r day-1-graphs}

# HNs

ggplot(data=day1HN_sex, aes(x=Genotype, y=len, fill = Genotype)) +
  geom_bar(stat="identity", width=0.5) +
  facet_grid(Sex~Treatment) + 
  labs(y="Average Percent Freezing Time", x='') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5) +
  theme_bw() +
  labs(title="Contextual Test", y="Mean Percent Freezing Time") +
  scale_fill_manual(values = c("#6a0dad", "#008000", "#FF0000"))

# non HN
ggplot(data=day1_nonHN, aes(x=Age_group, y=len, fill = Age_group)) +
  geom_bar(stat="identity", width=0.5) +
  facet_grid(Sex~Genotype) + 
  labs(y="Average Percent Freezing Time", x='') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5) +
  theme_bw() +
  labs(title="Contextual Test", y="Mean Percent Freezing Time") +
  scale_fill_manual(values =c("purple", "green"))
  
# non HN faceted by age group
ggplot(data=day1_nonHN, aes(x=Age_group, y=len, fill = Age_group)) +
  geom_bar(stat="identity", width=0.5) +
  facet_grid(Sex~Genotype) + 
  labs(y="Average Percent Freezing Time", x='') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5) +
  theme_bw() +
  labs(title="Contextual Test", y="Mean Percent Freezing Time")

# violin plot

day1HN_violin<-all_day1 %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
   mutate(Age_group = case_when(
    Age_Substracted < 9 ~ '6 months',
    Age_Substracted >= 9 | Age_Substracted <= 16 ~ '12 months',
    Age_Substracted >= 16 ~ "18 months"
  )) %>% 
  filter(Age_group == '12 months') %>% 
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  filter(!is.na(Sex)) %>% 
  select(Genotype, Pct.Total.Time.Freezing, Treatment, Sex) 

counts <- day1HN_violin %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  count(Genotype)
print(counts)

print(day1HN_violin)

poster<-day1HN_violin %>% 
  mutate(Treatment = case_when(
      Treatment=='HFD' ~ 'High Fat Diet',
      Treatment=='Control'~ 'Control'
  ))

# HN figure for paper
ggplot(data = poster, aes(factor(Genotype), Pct.Total.Time.Freezing)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  theme_bw()+
  facet_grid(Sex~Treatment) + 
  geom_jitter(height = 0, width = 0.3, size = 0.7, aes(color = Genotype)) +
  labs(y = "Mean Percent Freezing Time", x='') +
  scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000")) +
  labs(title='Contextual Test')

# non HN figure for paper
ggplot(data = day1_nonHN, aes(factor(Genotype), Pct.Total.Time.Freezing)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  theme_bw()+
  facet_grid(Sex~Treatment) + 
  geom_jitter(height = 0, width = 0.3, size = 0.7, aes(color = Genotype)) +
  labs(y = "Mean Percent Freezing Time", x='') +
  scale_color_manual(values = c("#1BCC97", "#1B50CC", "#CC1BA8")) +
  labs(title='Contextual Test')



```

```{r day-1-anova}
#print(day1_lm)

day1_lm<-all_day1 %>% 
  filter(!is.na(Animal_ID)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  select(Genotype, Treatment, Pct.Total.Time.Freezing) 

day1_hfd<-day1_lm %>% 
  filter(Treatment=="HFD")
day1_ctrl<-day1_lm %>% 
  filter(Treatment=="Control")

lm1_hfd <-lm(Pct.Total.Time.Freezing~factor(Genotype), day1_hfd)
lm1_ctrl <-lm(Pct.Total.Time.Freezing~factor(Genotype), day1_ctrl)

model1<-emmeans(lm1_hfd, "Genotype", adjust = "Tukey")
model2<-emmeans(lm1_ctrl, "Genotype", adjust = "Tukey")

pairs(model1)
pairs(model2)

```

```{r help-3}
day2_lm<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN")  %>% 
 # filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  filter(Treatment == 'Control') %>% 
  filter(comp == '1: Pre-Tone') %>% 
  group_by(Genotype, comp, Treatment) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

print(day2_lm)
```

```{r day-2-data}

day2_lm<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22" |
           Genotype == "APOE44HN") %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  select(Genotype, comp, Age_group, Pct.Total.Time.Freezing)

counts <- day2_lm %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  count(Genotype)
print(counts)



day2_age<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22" |
           Genotype == "APOE44HN")  %>%  
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  group_by(Genotype, comp, Age_group) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

day2_diet<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22" |
           Genotype == "APOE44HN") %>% 
  filter(!is.na(Age_group)) %>% 
  #filter(Age_group == '12 months') %>% 
  group_by(Genotype, comp, Treatment) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 

day2_nonhn<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE22" |
           Genotype == "APOE33" |
           Genotype == "APOE44") %>% 
  filter(!is.na(Age_group)) %>% 
  #filter(Age_group == '12 months') %>% 
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  filter(!is.na(Sex)) %>% 
  mutate(Treatment = case_when(
      Treatment=='HFD' ~ 'High Fat Diet',
      Treatment=='Control'~ 'Control'
  )) %>% 
  select(Genotype, comp, Treatment, Sex, Pct.Total.Time.Freezing)

day2_nonHN_bar<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE44" |
          Genotype == "APOE33" |
          Genotype == "APOE22")  %>% 
  filter(!is.na(Age_group)) %>% 
  #filter(Age_group == '12 months') %>% 
  group_by(Genotype, comp, Treatment) %>% 
  summarise(n=n(),
            se = sd(Pct.Total.Time.Freezing, na.rm=TRUE)/sqrt(n),
            len = mean(Pct.Total.Time.Freezing)) 


# HN 

hn_age <- day2_diet %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") 
  

non_hn <- day2_diet %>% 
  filter(Genotype == "APOE44" |
           Genotype == "APOE33" |
           Genotype == "APOE22") 
```

```{r day-2-graphs}

# HNs
day2_violin<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  filter(!is.na(Age_group)) %>% 
  #filter(Age_group == '12 months') %>% 
  mutate(Sex = case_when(
    Sex == 'male' ~ 'Male',
    Sex == 'female' ~ 'Female',
    Sex == 'Male' ~ 'Male',
    Sex == 'Female' ~ 'Female',
  )) %>% 
  filter(!is.na(Sex)) %>% 
  select(Genotype, comp, Treatment, Sex, Pct.Total.Time.Freezing)

poster<-day2_violin %>% 
  mutate(Treatment = case_when(
      Treatment=='HFD' ~ 'High Fat Diet',
      Treatment=='Control'~ 'Control'
  ))
print(poster)

pre<-poster %>% 
  filter(comp=='1: Pre-Tone')
tone<-poster %>% 
  filter(comp=='2: Tone')
post<-poster %>% 
  filter(comp=='3: Post-Tone')


ggplot(data = pre, aes(factor(Genotype), Pct.Total.Time.Freezing)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  facet_grid(Sex~Treatment) +
  theme_bw()+
  geom_jitter(height = 0, width = 0.3, aes(color = Genotype)) +
  labs(y = "Mean Percent Freezing Time", x='') +
  scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(title="Tone Test: pre-tone")

ggplot(data = tone, aes(factor(Genotype), Pct.Total.Time.Freezing)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  facet_grid(Sex~Treatment) +
  theme_bw()+
  geom_jitter(height = 0, width = 0.3, aes(color = Genotype)) +
  labs(y = "Mean Percent Freezing Time", x='') +
  scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(title="Tone Test: tone")

ggplot(data = post, aes(factor(Genotype), Pct.Total.Time.Freezing)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  facet_grid(Sex~Treatment) +
  theme_bw()+
  geom_jitter(height = 0, width = 0.3, aes(color = Genotype)) +
  labs(y = "Mean Percent Freezing Time", x='') +
  scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(title="Tone Test: post-tone")

# Violin for poster
ggplot(data = poster, aes(factor(Genotype), Pct.Total.Time.Freezing)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  facet_grid(Treatment~comp) +
  theme_bw()+
  geom_jitter(height = 0, width = 0.3, size = 0.7, aes(color = Genotype)) +
  labs(y = "Mean Percent Freezing Time", x='') +
  scale_color_manual(values = c("#6a0dad", "#008000", "#FF0000")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(title="Tone Test")

# Violin non HN for poster
ggplot(data = day2_nonhn, aes(factor(Genotype), Pct.Total.Time.Freezing)) +
  geom_violin() +
  geom_boxplot(width = 0.1) +
  facet_grid(Treatment~comp) +
  theme_bw()+
  geom_jitter(height = 0, width = 0.3, size = 0.7, aes(color = Genotype)) +
  labs(y = "Mean Percent Freezing Time", x='') +
  scale_color_manual(values = c("#1BCC97", "#1B50CC", "#CC1BA8")) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))+
  labs(title="Tone Test")

# bar plot HN for poster
ggplot(data=hn_age, aes(x=Genotype, y=len, fill=Genotype)) +
  geom_bar(stat="identity", width=0.5) +
  scale_fill_manual(values = c("#6a0dad", "#008000", "#FF0000"))+
  facet_grid(Treatment~comp) + 
  labs(y="Average Percent Freezing Time", x='') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5) +
  theme_bw() +
  labs(title="Tone Test", y='Mean percent time freezing') + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

# bar plot non HN for poster 
ggplot(data=day2_nonHN_bar, aes(x=Genotype, y=len, fill=Genotype)) +
  geom_bar(stat="identity", width=0.5) +
  scale_fill_manual(values = c("#1BCC97", "#1B50CC", "#CC1BA8"))+
  facet_grid(Treatment~comp) + 
  labs(y="Average Percent Freezing Time", x='') +
  geom_errorbar(aes(ymin=len-se, ymax=len+se), width=0.2, size=0.5) +
  theme_bw() +
  labs(title="Tone Test", y='Mean percent time freezing') + 
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5))

```

```{r day-2-anova}
#print(day2)

day2_lm<-all_day2 %>% 
  filter(!is.na(Trial)) %>% 
  mutate(comp = case_when(
    Component.Name == 'Day2_Acclimation' ~ '1: Pre-Tone',
    Component.Name == 'Day2_CSTone' ~ '2: Tone',
    Component.Name == 'Day2_Exploration' ~ '3: Post-Tone'
  )) %>% 
  filter(!is.na(comp)) %>% 
  filter(Genotype == "APOE22HN" |
           Genotype == "APOE33HN" |
           Genotype == "APOE44HN") %>% 
  #filter(Age_group == '12 months') %>% 
  filter(!is.na(Age_group)) %>% 
  select(Pct.Total.Time.Freezing, Genotype, Treatment, comp) 

pretone<-day2_lm %>% 
  filter(comp=='1: Pre-Tone')
tone<-day2_lm %>% 
  filter(comp=='2: Tone')
posttone<-day2_lm %>% 
  filter(comp=='3: Post-Tone')

hfd_2<-day2_lm %>% 
  filter(Treatment=="HFD")
control_2<-day2_lm %>% 
  filter(Treatment=='Control')

lm_pre<-lm(Pct.Total.Time.Freezing~Treatment+factor(Genotype), pretone)
lm_t<-lm(Pct.Total.Time.Freezing~Treatment+factor(Genotype), tone)
lm_post<-lm(Pct.Total.Time.Freezing~Treatment+factor(Genotype), posttone)

lm_hfd2<-lm(Pct.Total.Time.Freezing~factor(Genotype)+factor(comp), hfd_2)
lm_ctrl2<-lm(Pct.Total.Time.Freezing~Genotype+factor(comp), control_2)

anova(lm_hfd2)

model_hfd<-emmeans(lm_pre, "comp", adjust = "Tukey")
pairs(model_hfd)

model_ctrl<-emmeans(lm_pre, "comp", adjust = "Tukey")
pairs(model_ctrl)

model<-emmeans(lm_pre, "Genotype", adjust = "Tukey")
model_t<-emmeans(lm_t, "Genotype", adjust = "Tukey")
model_post<-emmeans(lm_post, "Genotype", adjust = "Tukey")

pairs(model)
pairs(model_t)
pairs(model_post)

```
